# audioBlastAnalyse
audioBlastAnalyse is an R package that handles the analysis of recordings. While some analyses (e.g. annotations) can be imported during the ingest process this is not true for all sources of recordings.

## Requirements
The analysis system requires a computer running the R environment for statistical computing. The package will import all dependencies on installation.

The package is tested on recent MacOS, Linux, and Windows systems.

If the analysis system is to write directly to the audioBlast database then it must additionally be on the NHM network (including via the VPN).

## Development
The package is hosted on the audioBlast GitHub at https://github.com/audioblast/audioBlastAnalyse.

## Installation
Installation of the package requires the devtools package.
```{r, eval=FALSE}
install.packages("devtools")
```

### From GitHub
```{r, eval=FALSE}
devtools::install_github("audioblast/audioBlastAnalyse")
```

### From R working directory
```{r, eval=FALSE}
devtools::install()
```
